Hedonic Analysis over Time and Space:\\ The Case of House Prices and Traffic Noise

### 2014-11-11 JRSarticle/text/NoiseHedonicFinal.Rnw
final edits? moved equation #s to left hand side and removed colons from bibliography
added acknowledgement of editor and referees plus Carleton College affiliation.

\documentclass{article}
\usepackage{floatpag} %floatpag.sty file is just in the reports folder - commands to remove page nos are in first figure
\usepackage[round]{natbib}
\usepackage{dcolumn}
\usepackage{pifont}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage[nolists]{endfloat}
\usepackage[width = 5.5in]{geometry}
\usepackage{caption, amsmath, graphicx, setspace, multirow, color, array}
\usepackage[hidelinks]{hyperref}

@@

\title{Hedonic Analysis over Time and Space:\\ The Case of House Prices and Traffic Noise}
\date{}
\author{Aaron Swoboda, Tsegaye Nega and Maxwell Timm}

>>>>

\documentclass[leqno]{article}
\usepackage{floatpag} %floatpag.sty file is just in the reports folder - commands to remove page nos are in first figure
\usepackage[round]{natbib}
\usepackage{dcolumn}
\usepackage{pifont}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage[nolists]{endfloat}
\usepackage[width = 5.5in]{geometry}
\usepackage{caption, amsmath, graphicx, setspace, multirow, color, array}
\usepackage[hidelinks]{hyperref}

@@

\title{Hedonic Analysis over Time and Space:\\ The Case of House Prices and Traffic Noise}
\date{}
\author{Aaron Swoboda, Tsegaye Nega and Maxwell Timm\thanks{The authors would like to thank Professor Steven Brakman and three anonymous referees for their helpful advice and comments.}
  \\ Carleton College \\  Northfield, MN 55057 \\
  aswoboda@carleton.edu \\
  tnega@carleton.edu \\
  maxgtimm@gmail.com
}
